The effects of binarity on planet occurrence rates measured by transit surveys

### 2017-11-14 paper/main.tex
remake model 1 Fig w/ smaller BF

This work aims to clarify the biases that stellar binarity introduces
to occurrence rates inferred from transit surveys.
In general, stellar multiplicity leads to diluted planetary 
radii, overestimated detection efficiencies, and an undercounted number of 
selected stars (but possibly an overcounted number of searched stars).
These effects skew occurrence rate measurements in different directions, and 
we develop simple models that allow us to understand the crucial effects.
For a model in which all stellar systems are either single or twin binaries, 
and all planets are identical, we find that ignoring binarity leads to an 
underestimate of the occurrence at the true radius by a multiplicative factor 
of $0.8$ (assuming a 10\% twin binary fraction).
Using more realistic models for the stellar population and planetary 
radii, we find that ignoring binarity leads to a $10$\,-\,$30\%$ 
underestimate of the number of planets per star, depending on the true radius 
distribution.
For the occurrence of Earth-sized planets, in our most realistic model the 
rate is underestimated by $\approx 15\%$~--~at present far smaller than 
systematic uncertainties on real $\eta_\oplus$ measurements.
For hot Jupiters, we find that the inferred occurrence rate is 
$\approx 1.3\times$ smaller than the true rate around single stars.
We suggest that this latter effect contributes to the discrepant hot Jupiter 
rates measured by {\it Kepler}\ and the California group's respective surveys.
\end{abstract}

>>>>

This work aims to clarify the biases that stellar binarity introduces
to occurrence rates inferred from transit surveys.
In general, stellar multiplicity leads to diluted planetary 
radii, overestimated detection efficiencies, and an undercounted number of 
selected stars (but possibly an overcounted number of searched stars).
These effects skew occurrence rate measurements in different directions, and 
we develop simple models that allow us to understand the crucial effects.
For a model in which all stellar systems are either single or twin binaries, 
and all planets are identical, we find that ignoring binarity leads to an 
underestimate of the occurrence at the true radius by a multiplicative factor 
of $0.76$ (assuming a 10\% twin binary fraction).
Using more realistic models for the stellar population and planetary 
radii, we find that ignoring binarity leads to a $10$\,-\,$30\%$ 
underestimate of the number of planets per star, depending on the true radius 
distribution.
For the occurrence of Earth-sized planets, in our most realistic model the 
rate is underestimated by $\approx 15\%$~--~at present far smaller than 
systematic uncertainties on real $\eta_\oplus$ measurements.
For hot Jupiters, we find that the inferred occurrence rate is 
$\approx 1.3\times$ smaller than the true rate around single stars.
We suggest that this latter effect contributes to the discrepant hot Jupiter 
rates measured by {\it Kepler}\ and the California group's respective surveys.
\end{abstract}

### 2017-11-14 paper/simplest_effects.tex
remake model 1 Fig w/ smaller BF

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        Inferred planet occurrence rates over $0.01r_\oplus$ bins in planet 
        radius,
        for Model \#1.
        This model has fixed stars, fixed planets, and twin binaries.
        If the true planet radius is $r_p$, all planets 
        detected in binaries will have apparent radii $r_a = r_p/\sqrt{2}$.
        To illustrate the individual biases, we 
        separated them.
        On this and future plots,
        ``only wrong $N_\star$'' means the only error is an incorrectly 
        assumed 
        number of selected stars;
        ``only wrong $Q$'' means the only error is an incorrectly assumed 
        completeness (including both miscalculated $p_{\rm tra}$ 
        and fraction of selected stars that are searchable, $p_{\rm det}$);
        ``only wrong $r_a$'' means the only error is in miscalculated        
        planetary radii, due to both transit depth dilution and also wrongly 
        assumed host star radii.
    }
    \label{fig:errcases_model_1}
\end{figure}

@@

If we continue assuming that the number of planets per single, primary, and 
secondary star are equal ($Z_0=Z_1=Z_2$), we find a rate density correction 
factor at the true planet radius of
\begin{equation}
X_\Gamma(r_p) = \frac{1}{1+\mu},
\label{eq:Z_eq_model_1_correction}
\end{equation}
This yields a correction of 0.79 if ${\rm BF}=0.1$, and 0.88 if ${\rm 
BF}=0.05$.
Rephrasing the result, if the twin binary fraction were 
$(2^{3/2}+1)^{-1}\approx 0.26$, then the apparent rate would be half the true 
rate.
Fortunately, in most contexts the twin binary fraction is not that high.

>>>>

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/errcases_rate_density_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        Inferred planet occurrence rates over $0.01r_\oplus$ bins in planet 
        radius,
        for Model \#1.
        This model has fixed stars, fixed planets, and twin binaries. 
        It assumes a twin binary fraction of ${\rm BF}=0.1$.
        If the true planet radius is $r_p$, all planets 
        detected in binaries will have apparent radii $r_a = r_p/\sqrt{2}$.
        We illustrate the individual biases by separating them.
        On this and future plots,
        ``only wrong $N_\star$'' means the only error is an incorrectly 
        assumed 
        number of selected stars;
        ``only wrong $Q$'' means the only error is an incorrectly assumed 
        completeness (including both miscalculated $p_{\rm tra}$ 
        and fraction of selected stars that are searchable, $p_{\rm det}$);
        ``only wrong $r_a$'' means the only error is in miscalculated        
        planetary radii, due to both transit depth dilution and also wrongly 
        assumed host star radii.
    }
    \label{fig:errcases_model_1}
\end{figure}

@@

If we continue assuming that the number of planets per single, primary, and 
secondary star are equal ($Z_0=Z_1=Z_2$), we find a rate density correction 
factor at the true planet radius of
\begin{equation}
X_\Gamma(r_p) = \frac{1}{1+\mu},
\label{eq:Z_eq_model_1_correction}
\end{equation}
This yields a correction of 0.76 if ${\rm BF}=0.1$, and 0.87 if ${\rm 
BF}=0.05$.
Rephrasing the result, if the twin binary fraction were 
$(2^{3/2}+1)^{-1}\approx 0.26$, then the apparent rate would be half the true 
rate.
Fortunately, in most contexts the twin binary fraction is not that high.
